Atmospheric escape and star-planet-interaction in the HAT-P-67 b system

### 2022-11-14 paper/paper1/ms.tex
TESS 2-minute cadence has about 1 ppt RMS

\subsection{TESS Light Curve}
HAT-P-67 was observed with the \emph{Transiting Exoplanet Survey Satellite} \citep[TESS][]{2014SPIE.9143E..20R} in Sectors 24, 26, 51, 52, 53 with 2-minute cadence.

@@

@@

We observed the HAT-P-67 system using data from TESS Sector 24 taken from April 16th, 2020 to May 13th, 2020 with an exposure time of 1800 seconds. Using the \texttt{lightkurve} package, we attempted to phase fold our exoplanet transit plot to identify the stellar rotation signal and the exoplanet's transit signal. At first glance, the stellar flux decreases by about 0.2\% and the exoplanet transit signal decreases by about 0.7\%. In order to analyze the stellar rotation period, we must mask the planetary transit signal. By folding the normalized lightcurve with a given planetary orbital period of 4.810 days, we omitted the planetary transit signal. We then created a periodogram of just the stellar signal and arrived at an estimate of several parameters for HAT-P-67b: the planetary period is 4.809 days, the original transit time was 1958.082 BTJD, and the planetary duration was 0.25 days. We then created a cadence mask using the Box Least Squares parameters. The resulting periodogram of just the stellar variation described a rotational period of 5.417 days is shown in Figure \ref{fig:stellar_periodogram}.

\subsubsection{Revised exoplanet parameters with exoplanet framework}

@@

\software{  \texttt{pandas} \citep{mckinney10},
    \texttt{emcee} \citep{foreman13},
    \texttt{matplotlib} \citep{hunter07},
    \texttt{numpy} \citep{2020NumPy-Array},
    \texttt{scipy} \citep{2020SciPy-NMeth},
    \texttt{ipython} \citep{perez07},
    \texttt{seaborn} \citep{waskom14},
    \texttt{astropy} \citep{2013A&A...558A..33A,2018AJ....156..123A},
    \texttt{muler} (Gully-Santiago et al., submitted),
    \texttt{telfit} \citep{2014AJ....148...53G},
    \texttt{jupyter} \citep{Kluyver2016jupyter}}

>>>>

\subsection{TESS Light Curve}
HAT-P-67 was observed with the \emph{Transiting Exoplanet Survey Satellite} \citep[TESS][]{2014SPIE.9143E..20R} in Sectors 24, 26, 51, 52, 53 with 2-minute cadence, and in Sector 25 with 30-minute (FFI) cadence.

@@

\subsubsection{Revised exoplanet parameters with exoplanet framework}
We assembled a composite lightcurve from TESS Sectors 24, 26, 51, 52, 53, which were reduced with the default SPOC pipeline \citep{2020RNAAS...4..201C}.  These TESS data exhibit a native RMS scatter of better than 1 part-per-thousand (ppt).  We fit a Keplerian orbit model to the TESS lightcurve using the \texttt{exoplanet} framework \citep{exoplanet:joss}.

Using the \texttt{lightkurve} package, we attempted to phase fold our exoplanet transit plot to identify the stellar rotation signal and the exoplanet's transit signal. At first glance, the stellar flux decreases by about 0.2\% and the exoplanet transit signal decreases by about 0.7\%. In order to analyze the stellar rotation period, we must mask the planetary transit signal. By folding the normalized lightcurve with a given planetary orbital period of 4.810 days, we omitted the planetary transit signal. We then created a periodogram of just the stellar signal and arrived at an estimate of several parameters for HAT-P-67b: the planetary period is 4.809 days, the original transit time was 1958.082 BTJD, and the planetary duration was 0.25 days. We then created a cadence mask using the Box Least Squares parameters. The resulting periodogram of just the stellar variation described a rotational period of 5.417 days is shown in Figure \ref{fig:stellar_periodogram}.

@@

@@

\software{  \texttt{pandas} \citep{mckinney10},
    \texttt{emcee} \citep{foreman13},
    \texttt{matplotlib} \citep{hunter07},
    \texttt{numpy} \citep{2020NumPy-Array},
    \texttt{scipy} \citep{2020SciPy-NMeth},
    \texttt{ipython} \citep{perez07},
    \texttt{seaborn} \citep{waskom14},
    \texttt{astropy} \citep{2013A&A...558A..33A,2018AJ....156..123A},
    \texttt{muler} (Gully-Santiago et al., submitted),
    \texttt{telfit} \citep{2014AJ....148...53G},
    \texttt{exoplanet} \citep{exoplanet:joss},
    \texttt{jupyter} \citep{Kluyver2016jupyter},
}
